\documentclass[12pt, titlepage]{article}

\usepackage{longtable}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=ForestGreen,
	filecolor=WildStrawberry,
	linkcolor=Purple,
	urlcolor=Cerulean
}
\usepackage[round]{natbib}
\usepackage{float}
\usepackage{adjustbox}

\usepackage{xr}
\externaldocument{../SRS/SRS}
\newcommand{\rref}[1]{R\ref{#1}}

\externaldocument{../Design/MIS/MIS}
\newcommand{\misref}[1]{MIS: \ref{#1}}

\input{../Comments}

\begin{document}

\title{Test Report: Companion Cube Calculator} 
\author{Geneva Smith}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
December 19, 2017 1 & 1.0 & Completed the initial test report\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{Symbol} & \textbf{Description}\\
  \midrule 
  MIS & Module Interface Specification \\
  R & Requirement \\
  T & Test\\
  \bottomrule
\end{tabular}\\

\newpage

\tableofcontents

\listoftables %if appropriate

%\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

\section{Introduction}
This is the test report for the Companion Cube Calculator, a mathematical 
tool which determines the range of a user-specified function given the domains 
of the function's variables. The the directory for this project can be found at:

\begin{center}
	\href{https://github.com/GenevaS/CAS741}{https://github.com/GenevaS/CAS741}.
\end{center} 

\section{Functional Requirements Evaluation}

The following tests have failed by verification:

	\begin{center}
		\begin{longtable}{ | p{3cm} | p{3cm} | p{2cm} | p{2cm} | p{3cm} |}
			\caption{Failed Functional Test Summary} \\ \hline 
			\label{TblInputVar} 
			ID & Input & Expected Outcome & Expected MsgID & Actual MsgID \\ 
			\hline
			test-control\_ precedenceOfOperators3 & 
			\texttt{"x\textasciicircum2*y", 
				"x,2,4\textbackslash ny,3,5"}, 
				\texttt{"(x\textasciicircum2)*y", 
				"x,2,4\textbackslash ny,3,5"} & $TRUE$ & - & (EQC\_ 
				INCOMPLETE\_OP) 
			Error: Unrecognized sequence encountered during Atomic Equation 
			parsing. Remaining equation = \texttt{)*y}. \\ \hline
			
			test-control\_ precedenceOfOperators6 & 
			\texttt{"(2(x+y)\textasciicircum2) /(3\textasciicircum z)", 
				"x,1,2\textbackslash ny,3,4 \textbackslash nz,5,6"} & 
			\texttt{"[0.0438 9574759945 13, \textbackslash n 0.2962962 
			96296296]"} 
			& 
			Range calculated successfully. & (EQC\_ INCOMPLETE\_OP) Error: 
			Unrecognized sequence 
			encountered during Atomic Equation parsing. Remaining equation = 
			\texttt{)/(3\textasciicircum z)}. \\ \hline
		\end{longtable}
	\end{center}


\section{Non-Functional Requirements Evaluation}
The non-functional requirements were not always easy to verify. Some, such as 
robustness, could be adequately verified using the existing test suites. 
Others, such as correctness and usability, required manual testing. Not all 
non-functional requirements were verified in this project cycle due to time 
constraints.

\subsection{Correctness}
Correctness testing could not be completed in this project cycle due to time 
constraints.

These tests are directly related to \rref{R_conditionfx} and 
\rref{R_CalculateCompose} (Decomposing the user equation into components and 
recomposing the results).

\subsection{Robustness}
The robustness requirement for recognizing violated data constraints was 
covered in the functional tests:

\begin{itemize}
	\item The constraints on supported operators are contained in the Range 
	Solver test suite. The containment of all operator-specific information 
	within this module made it possible to collect all of these restrictions in 
	the same suite. This design also implicitly supported the output constraint 
	on $R(f(V))$ because only mathematical operations that produced closed, 
	real intervals were implemented.
	\item The constraint of having every $D(v) \in V$ defined as a closed, real 
	interval are contained in the Interval Conversion and Interval Data 
	Structure modules.
\end{itemize}

These tests are directly related to \rref{R_verifyinputs} and 
\rref{R_VerifyOutputConstraints} (Verifying that the program satisfies the 
input and output constraints).

\subsection{Verifiability}
The verifiability requirement stated that the program must be created in a way 
in which its calculations can be checked for correctness. By basing this design 
on verifiable mathematical concepts and implementing the equation decomposition 
using a grammar definition, it is possible to measure if this requirement has 
met. However, verifiability testing could not be completed in this project 
cycle due to time constraints.

This is indirectly related to \rref{R_Output} because the outputs must be shown 
to the program user such that they understand and have confidence in the 
program's results.

\subsection{Usability}
The usability requirements were verified using the informal user study 
described in the test plan. There were five participants.

All participants calculated the same range of their assigned equation within 
nine significant figures. Differences in the values could be attributed to the 
specifications of individual machines. Since floating-point error handing is 
not considered an important aspect of this program, variations beyond nine 
significant digits were not deemed unacceptable.

In general, participants found it easy to find and use the input mechanisms on 
the GUI for entering in their values directly and for loading data from a file 
(Table~\ref{TblUserResponses}). 

\begin{center}
	\begin{longtable}{ | p{2.5cm} | p{1.5cm} | p{1.1cm} | m{1.5cm} | m{1.6cm} 
			|m{1.5cm} |m{1.5cm} |}
		\caption{Summary of User Responses} \\ \hline \label{TblUserResponses} 
		& \textbf{Strongly Agree} & \textbf{Agree} & \textbf{Neutral} & 
		\textbf{Disagree} & \textbf{Strongly Disagree} & \textbf{No Response}  
		\\ 
		\hline
		Finding Equation Input Mechanism & 4 & 1 & 0 & 0 & 0 & 0 \\ 
		\hline
		
		Using Equation Input Mechanism& 3 & 0 & 2 & 0 & 0 & 0 \\  \hline
		
		Finding Variable Input Mechanism& 5 & 0 & 0 & 0 & 0 & 0 \\  \hline
		
		Using Variable Input Mechanism& 4 & 0 & 1 & 0 & 0 & 0 \\  \hline
		
		Finding Load From File Option& 3 & 2 & 0 & 0 & 0 & 0 \\  \hline
		
		Finding the Calculated Range& 4 & 0 & 0 & 0 & 0 & 1 \\  \hline
		
		Understanding the Calculated Range& 4 & 0 & 0 & 0 & 0 & 1 \\  \hline
		
		Understanding the Program Workflow& 3 & 1 & 0 & 1 & 0 & 0 \\  \hline
	\end{longtable}
\end{center}

For responses that were unfavourable towards the program's usability, a number 
of suggestions were left to help improve the experience. The simplest 
improvement to do is to make the range values copyable. Currently, the output 
mechanism is a non-editable label, which does not support text selection. This 
can be improved by changing it to a non-editable text box instead.

While generally well received, one participant suggested that the ``Load from 
File" functionality could be accessible from a button located next to the 
equation input mechanism. This change would make it much easier to find the 
option to do so without prompting, and its inclusion will be considered in 
future GUI iterations.

The last suggested improvement was for the variable information table. The 
first identified problem was that a cursor does not appear until a cell is 
triple-clicked, which is unusual for text entry fields. Another problem was 
that text entry did not automatically move to the next cell in the table so 
that they could enter in variables as they appeared in the task description. 
Unfortunately, this is a limitation on the available GUI widgets and no further 
improvements can be done within the scope of the program. If an improved table 
entry mechanism is created for Windows GUI applications, these usability issues 
can be addressed.

Another problem that was identified for the variable data tabe was that an 
extra row appeared at the bottom of the table even when no more variables were 
required. They suggested an alternate such that an ``Add Variable" button is 
required to add new table rows. Given the other work flow issues that have been 
raised with this particular mechanism, the suggested alternative is a viable 
option for future GUI design iterations.

In addition to work flow and GUI mechanism issues, the user study also 
uncovered an error with the program where extra, but valid, brackets were used. 
Test cases to detect this situations have since been added to the test suite, 
and are currently the only tests that are failing (Table~\ref{TblInputVar}).
		
\subsection{Maintainability}
The maintainability requirements focus on the extensibility of the original 
implementation with respect to its supported mathematical operations. Support 
for open, real intervals already exists in the Interval Conversion and Interval 
Data Structure modules. This means that it is possible that only the Range 
Solver module would need to be updated to add more mathematical operations. 
However, maintainability testing could not be completed in this project cycle 
due to time constraints.

\section{Unit Testing}
In addition to the functional requirements, unit tests were implemented to 
achieve 100\% code coverage in all documented modules. The purpose of this was 
to ensure that all code paths, including conditional branches, were being 
executed and to help identify program errors that were not covered in the 
functional testing suite. Implementation files that were automatically 
generated or that were added to implement the GUI are not covered in the unit 
tests.

\begin{center}
		\begin{longtable}{ | p{2.5cm} | p{4cm} | p{2.5cm} | m{1cm} | m{1.5cm} 
		|}
		\caption{Unit Test Summary} \\ \hline \label{TblUnitTests} 
		\textbf{Test Suite} & \textbf{Test File} & \textbf{Target Modules} & 
		\textbf{Total Tests} & 
		\textbf{Tests Passing (\%)}  \\ 
		\hline
		Control Flow & \texttt{ControlTests.cs} & ControlFlow 
		(\misref{Module_controlflow}) & 6 & 100\% \\ 
		\hline
		
		User Input & \texttt{InputTests.cs} &Input (\misref{Module_userinput}) 
		& 10 & 100\% \\ \hline
		
		Interval & \texttt{IntervalTests.cs} &Interval Data Structure 
		(\misref{Module_intervaldatastructure}), Interval Conversion 
		(\misref{Module_intervalconversion}) & 7 & 100\% \\ \hline
		
		Equation & \texttt{EquationTests.cs} &Equation Data Structure 
		(\misref{Module_equationdatastructure}), Equation Conversion 
		(\misref{Module_equationconversion}) & 16 & 100\% \\ \hline
		
		Variable Consolidation & \texttt{VariableConsoli dationTests.cs} & 
		Consolidate 
		(\misref{Module_variableconsolidation}) & 8 & 100\% \\ \hline
		
		Solver &\texttt{SolverTests.cs} & Operator Data Structure 
		(\misref{Module_operatordatastructure}), Solver 
		(\misref{Module_rangesolver}) & 17 & 100\% \\ \hline
		
		Output & \texttt{OutputTests.cs} &Output (\misref{Module_output}) & 6 & 
		100\% \\ \hline
	\end{longtable}
\end{center}

\section{Changes Due to Testing}
The test suites uncovered a number of bugs, most of which resulted in changes 
to the equation parsing process in the Equation Conversion module 
(\misref{Module_equationconversion}). The failed functional tests have 
identified an additional parsing error that will be corrected in a future 
project cycle.

The user study also uncovered a number of failings, including the inability to 
copy the range values, which will also be addressed in a future project cycle.

\section{Automated Testing}
All automated testing was performed using the unit testing framework available 
in Visual Studio 2017 (Enterprise Edition). The associated project is 
\texttt{UnitTests\_CompanionCubeCalculator.csproj}.
		
\section{Trace to Requirements}

\begin{table}[H]
	\centering
	\rotatebox{-90}{
		\scalebox{0.85}{
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			& \rref{R_Inputs}& \rref{R_conditionX} & \rref{R_verifyinputs}& 
			\rref{R_conditionfx} & \rref{R_Calculate}& 
			\rref{R_CalculateCompose}& 
			\rref{R_VerifyOutput} & \rref{R_VerifyOutputConstraints}& 
			\rref{R_Output} & NF: Robustness & NF: Usability\\
			\hline
			Control Flow & X & & & & & &  &&&X&X\\ \hline
			User Input & X & & & & & & &&&&X\\ \hline 
			Interval & & X & X & & & & &&&X&\\ \hline
			Equation & & & & X & &&&& &X &\\ \hline
			Variable Consolidation & & & X &  &&& & & &&\\ \hline
			Solver & & &X &  & X & X & X & X & &X&\\ \hline
			Output & & & & & & &&&X &&X\\ 
			\hline
		\end{tabular}}}
	\caption{Traceability Matrix Showing the Connections Between Requirements 
		and Test Suites}
	\label{Table:R_trace}
\end{table}
		
\section{Trace to Modules}	
	\begin{table}[H]
		\centering
		\rotatebox{-90}{
			\scalebox{0.88}{
		\begin{tabular}{|c|c|c|c|c|c|c|c|}
			\hline
			& Control Flow & User Input & Interval & Equation & Variable 
			Consolidation& Solver	& Output \\
			\hline
			\misref{Module_controlflow}& X & & & &&&\\ \hline
			\misref{Module_userinput}& X & X & & & && \\ \hline 
			\misref{Module_intervalconversion}&  & & X & &X&&\\ \hline
			\misref{Module_equationconversion}&  & & & X &X &&\\ \hline
			\misref{Module_variableconsolidation}& X & & &&X&&\\ 
			\hline
			\misref{Module_rangesolver}& X & & & & &X& \\ \hline
			\misref{Module_output}& X & & & & && X\\ \hline
			\misref{Module_intervaldatastructure}& X & &X&&X&X &X \\ \hline
			\misref{Module_equationdatastructure}& X & & & X&X&X&X\\\hline
			\misref{Module_operatordatastructure}& & & &X &X &X&\\ 
			\hline
		\end{tabular}}}
		\caption{Traceability Matrix Showing the Connections Between 
		Modules	and Test Suites}
		\label{Table:M_trace}
	\end{table}


\section{Code Coverage Metrics}
A coverage of 100\% has been achieved for all documented modules. Code coverage 
was not considered for additional files that were created to support the GUI.

\end{document}